A data-intensive assessment of the species-abundance distribution.

### 2015-03-19 defense_pres.tex
More bits on data and analysis.

@@

\subsection{Analysis}
\begin{frame}[shrink=10]
\frametitle{SAD Comparisons}
~\\
~\\
Selected five models from four classes for comparison.
\begin{table}
\begin{tabular}{l|l}
 Model class & Form of the distribution\\ 
\hline
 Purely statistical & Logseries, Poisson lognormal\\
 Branching process & Zipf \\
 Population dynamics & Negative binomial\\
 Niche partitioning & Geometric \\
\end{tabular}
~\\
~\\
~\\
~\\
\caption{After B.J. McGill et al. 2007. Species abundance distributions: moving beyond single prediction theories to integration within an ecological framework. Ecology letters 10: 995-1015.}
\end{table}
\end{frame}

\begin{frame}[shrink=35]
\frametitle{SAD Comparisons}
\begin{center}
\begin{table}
\begin{tabular}{l|c|l|r}
 Dataset &Dataset code &Availability &Total sites\\
\hline
 Breeding Bird Survey &BBS &Public &2769\\
 Christmas Bird Count &CBC &Private &1999\\
 Gentry's Forest Transects &Gentry &Public &10355\\
 Forest Inventory Analysis &FIA	 &Public &220\\
 Mammal Community Database &MCDB &Public &103\\
 N. American Butterfly Count &NABA &Private &400\\
 Actinopterygii, this dissertation	 &Actinopterygii &Public &161\\
 Reptilia, this dissertation &Reptilia &Public &138\\
 Amphibia, this dissertation &Amphibia &Public &43\\
 Coleoptera, this dissertation &Coleoptera &Public &5\\
 Arachnida, this dissertation &Arachnida &Public &25\\
\end{tabular}
\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private were obtained through data requests to the providers resulting in Memorandums of Understanding governing data use.}
\end{table}
\end{center}
\end{frame}

>>>>

\subsection{Data Availability}
\begin{frame}[t]
\frametitle{Data}
~\\
~\\
The final community abundance database is publicly available and importable through the EcoData Retriever.\\ 
(http://www.ecodataretriever.org/)
\end{frame}

@@

\subsection{Data & Analysis}
\subsubsection{Model selection}
\begin{frame}[shrink=10]
\frametitle{SAD Comparisons}
~\\
~\\
Selected five models from four classes for comparison.
\begin{table}
\begin{tabular}{l|l}
 Model class & Form of the distribution\\ 
\hline
 Purely statistical & Logseries, Poisson lognormal\\
 Branching process & Zipf \\
 Population dynamics & Negative binomial\\
 Niche partitioning & Geometric \\
\end{tabular}
~\\
~\\
~\\
~\\
\caption{After B.J. McGill et al. 2007. Species abundance distributions: moving beyond single prediction theories to integration within an ecological framework. Ecology letters 10: 995-1015.}
\end{table}
\end{frame}

\subsubsection{Analysis}
\begin{frame}
\frametitle{SAD Comparisons}
~\\
Analysis:
\begin{itemize}
\item Model fitting with maximum likelihood estimation. 
\item Likelihood based model selection to compare the fits of the different models.
\item Model comparison with corrected Aikaike Information Criterion (AICc) weights.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SAD Comparisons}
~\\
Computational tools:
\begin{itemize}
\item Model fitting, log-likelihood, and AICc calculations performed with macroecotools Python package.\\
\begin{small}
(https://github.com/weecology/macroecotools)
\end{small}
\item All of the analysis code and the majority of the data is publicly available.
\begin{small}
(https://github.com/weecology/sad-comparison)
\end{small}
\end{itemize}
\end{frame}

\subsubsection{Data}
\begin{frame}[shrink=35]
\frametitle{SAD Comparisons}
\begin{center}
\begin{table}
\begin{tabular}{l|c|l|r}
 Dataset &Dataset code &Availability &Total sites\\
\hline
 Breeding Bird Survey &BBS &Public &2769\\
 Christmas Bird Count &CBC &Private &1999\\
 Gentry's Forest Transects &Gentry &Public &10355\\
 Forest Inventory Analysis &FIA	 &Public &220\\
 Mammal Community Database &MCDB &Public &103\\
 N. American Butterfly Count &NABA &Private &400\\
 Actinopterygii, this dissertation	 &Actinopterygii &Public &161\\
 Reptilia, this dissertation &Reptilia &Public &138\\
 Amphibia, this dissertation &Amphibia &Public &43\\
 Coleoptera, this dissertation &Coleoptera &Public &5\\
 Arachnida, this dissertation &Arachnida &Public &25\\
\end{tabular}
\caption{Datasets used for species-abundance distribution comparisons. Datasets marked as Private were obtained through data requests to the providers resulting in Memorandums of Understanding governing data use.}
\end{table}
\end{center}
\end{frame}
